---
title: "DESeq2Update"
output: html_notebook
---
# Recap: Organized htseq.counts files into ascending and sigmoid groups by renaming the files. 

Reading Count Data
# Set up the working directory to be where all the files downloaded in respective folders. Should be ~/Users/username/desktop/final_project/
```{r}
directory <- ('/Users/CrystalRubalcava/Desktop/final_project/')
```


Organize and Rename Count Data for easier recognition
#The htseq counts files for Stage II Colon Cancer are downloaded from National Cancer Institute's Genomic Data Commons (GDC) portal. There is data in these files that is either from patients with tumor origin sites in the sigmoid or ascending regions of the colon. 

# Rename htseq files for organization of ascending tumor origin sites
```{r}
#ht-seq data can be found using the gdc portal and filtering for stage II colon cancer with tumor site originating in ascending colon.
# below are all the extracted htseq.counts.txt files that were extracted from the 36 cases associated with ascending colon origin

directory <- ('/Users/CrystalRubalcava/Desktop/final_project/Ascending')

file <- c("056fe861-9f3b-4693-999a-44d1d7c43ab0.htseq.counts.txt",
"066a17b9-c724-4390-9a5f-d46cde556de3.htseq.counts.txt",
"082a0dad-65e5-49f2-955b-ca23831b2733.htseq.counts.txt",
"08dd2c8c-537f-4d02-a4b8-9c123156f0d4.htseq.counts.txt",
"0ed65bdf-cb92-47c1-8aeb-42518ce639b8.htseq.counts.txt",
"1580243c-8353-4c6e-a532-81121b912c21.htseq.counts.txt",
"171f6436-748a-4072-9ef6-e90d8cd9b465.htseq.counts.txt",
"1c48525e-6f1c-4ca0-9bb4-a9350cbca89f.htseq.counts.txt",
"25b8756b-61b5-40f8-bbdf-7b2de810c92f.htseq.counts.txt",
"2abfe58f-f168-413f-a56f-4c3c2aedbe3d.htseq.counts.txt",
"2f05c173-adfa-40c3-baf8-02563270ff3e.htseq.counts.txt",
"36263f87-1956-499c-ac90-dee060c5bdd4.htseq.counts.txt",
"37d2cb9b-0286-43a5-9538-26a8f0818ee7.htseq.counts.txt",
"4e7c6811-88e4-4bb7-a88f-7491dfa6d072.htseq.counts.txt",
"5b9b9a3d-51bf-4f62-bf19-7c7ea0267030.htseq.counts.txt",
"6f4f4e5d-d81e-402e-859f-3ee580a8bbde.htseq.counts.txt",
"6f90946a-0a30-49e8-8699-7a8890c01aed.htseq.counts.txt",
"73ce143e-44f1-49c6-963f-45246d8551de.htseq.counts.txt",
"81a64df9-c073-4097-ba73-896396da3135.htseq.counts.txt",
"81d8c120-144f-4ffc-9ca4-eb76ca1fc821.htseq.counts.txt",
"8e0528dd-5f85-4f48-937c-9e1455fbda78.htseq.counts.txt",
"938e4a22-7ed8-4b09-aa65-0cd737beee31.htseq.counts.txt",
"9556ee31-e56f-4611-9d37-2b4d19841d15.htseq.counts.txt",
"96f97dd0-3c7a-4a8c-a165-9ab14c9fcef6.htseq.counts.txt",
"9c64a139-1417-4465-8472-b44182874b0a.htseq.counts.txt",
"9e97f017-6855-4d68-bd2a-c4da3ccb1d57.htseq.counts.txt",
"a046b793-0eda-4c57-adfe-b8800ece1dab.htseq.counts.txt",
"b1a7e378-a07b-4434-8a5d-d4756b7d523c.htseq.counts.txt",
"ba11a188-132a-4a25-b2b7-f958694976e8.htseq.counts.txt",
"bdc7d801-b93b-4464-89b6-0148d066c947.htseq.counts.txt",
"bf8d10e1-1241-48fa-95a2-9e97fc58c17a.htseq.counts.txt",
"c2357737-ad60-4603-9ce3-4b30cc45d30b.htseq.counts.txt",
"c6972d82-17ef-4d72-8827-a5305d55f784.htseq.counts.txt",
"cecce47d-5d1a-4473-bf62-48b9bf602534.htseq.counts.txt",
"d1878265-460d-4768-a67d-73d8d5a315b7.htseq.counts.txt",
"d265829a-9e49-4e21-ba72-67f5ba406204.htseq.counts.txt",
"d5607680-758b-4ee5-ae0f-a61f7c3133c1.htseq.counts.txt",
"db9a7c76-8e42-4f1a-81a3-a9d4eb5365aa.htseq.counts.txt",
"e02d06a3-99f9-49ae-b3b0-c4427951789d.htseq.counts.txt",
"e158f016-7605-45b7-8e4f-bbe313fc461c.htseq.counts.txt",
"e82223ad-33c0-47fd-b0f2-982da64d0cb2.htseq.counts.txt",
"ec78640c-f4de-4d18-bf7c-9e5391feb915.htseq.counts.txt",
"ee4dcccc-514b-4cc6-ae63-6ed3e7519a40.htseq.counts.txt",
"ef4fdb47-ab17-4055-b8a5-ec3c2a4b7041.htseq.counts.txt",
"f36f74a9-97b4-4913-86e2-56ebaf55f006.htseq.counts.txt",
"f5c9ea63-ff66-441a-9a6b-055fdcd7cae9.htseq.counts.txt",
"fabefb10-5546-4017-8ea1-29982a10fb3c.htseq.counts.txt",)

# rename the file by adding the ```ascending``` to the end of the file name
# If TRUE returns, this means the file name change was successful, if else, the file will state that is does not exist.
if (file.exists(file)) {

 file.rename("*/.htseq.counts.txt", "*/ascending.counts.txt")

} else {

 cat("The file does not exist")

}
```

# Rename htseq files for organization of sigmoid tumor origin sites
```{r}
#ht-seq data can be found using the gdc portal and filtering for stage II colon cancer with tumor site originating in sigmoid colon.
# below are all the extracted htseq.counts.txt files that were extracted from the 36 cases associated with sigmoid colon origin

directory <- ('/Users/CrystalRubalcava/Desktop/final_project/Sigmoid')


file <- c("1b563146-6ead-41ba-9117-c9b1c5d4127f.htseq.counts.txt",
"020aa019-a3a4-4055-92ee-be824a597501.htseq.counts.txt",
"0422da40-5671-48c5-bbe0-e32a476c5cda.htseq.counts.txt",
"05eef9f8-a246-403a-b0be-07d274b6f93a.htseq.counts.txt",
"161caa2d-589a-4834-9073-3824031da5e6.htseq.counts.txt",
"17510ea6-0c97-4bd0-94a4-63dd76e5b7c7.htseq.counts.txt",
"20a523cd-58e9-467d-bed5-1bce2a8574f8.htseq.counts.txt",
"30cb2eed-e635-466d-85cb-6e3d00828688.htseq.counts.txt",
"3254c984-f9ec-4db5-9add-94489e000a62.htseq.counts.txt",
"3793cde5-8027-46ad-9003-6a9a43076764.htseq.counts.txt",
"4410295f-d9fc-43b6-8064-17ec17d5fb17.htseq.counts.txt",
"562e2cb3-078f-4796-b8a2-a0196713ebac.htseq.counts.txt",
"5654a36c-4d18-4746-8a4c-b7b616f99481.htseq.counts.txt",
"583c83ca-b9dd-46d2-811d-a4cde176ee24.htseq.counts.txt",
"59608767-595f-402a-9f7f-356dd6e99a51.htseq.counts.txt",
"5ac3599c-0254-4931-8dc8-3c3294be3cd7.htseq.counts.txt",
"5e2b0dc5-c09b-4334-9f2f-c8e75380d45c.htseq.counts.txt",
"67d1e5e4-91de-43df-b127-ffeef6070603.htseq.counts.txt",
"692efd81-4aba-45fb-a7fd-35c10c79ebf2.htseq.counts.txt",
"6ae2dd6c-2a39-411f-a1fc-11e0e6e82165.htseq.counts.txt",
"6e2db920-dc3e-4a74-8cdb-470cb61e2fac.htseq.counts.txt",
"708a16a3-7a5e-4e27-b06b-4c3c308b11fe.htseq.counts.txt",
"7324b2d6-dd30-4f99-a101-7c3d497bbcb8.htseq.counts.txt",
"77dbc29d-e3dd-45cc-b1d8-3bdd1711c704.htseq.counts.txt",
"789db3c8-c5cd-428d-aaef-e3f60c40bc9a.htseq.counts.txt",
"7b2cd944-1cd6-4107-8aa6-11913ee32257.htseq.counts.txt",
"80592959-da54-41d0-9b82-ed279be3ecea.htseq.counts.txt",
"82e00e45-734c-471f-ba97-79ec3b7e0baa.htseq.counts.txt",
"92107b4f-bd77-4401-9065-4b9704110d44.htseq.counts.txt",
"9f43c5bf-0fc1-4339-81a2-1d315d6940e7.htseq.counts.txt",
"b57f69a6-91ca-4131-a654-5495f6dd1131.htseq.counts.txt",
"c264fe3b-482b-44ec-83a4-73df565663ff.htseq.counts.txt",
"c3f9ba64-6946-45d4-984d-b33ef2589603.htseq.counts.txt",
"c3fe7418-c082-4c77-96f7-f22bd6210139.htseq.counts.txt",
"d62ce057-d970-4bb0-b929-923c7bfb9e11.htseq.counts.txt",
"de796614-444b-4e3e-b4e6-fb3a78ef6f65.htseq.counts.txt",
"f346f2d2-285c-455c-ba34-ea8eec3fa881.htseq.counts.txt",
"f38b2f21-c5a5-4699-9727-eae9c96aac55.htseq.counts.txt",)


# rename the file by adding the ```ascending``` to the end of the file name
# If TRUE returns, this means the file name change was successful, if else, the file will state that is does not exist.
if (file.exists(file)) {

 file.rename("*/.htseq.counts.txt", "*/sigmoid.counts.txt")

} else {

 cat("The file does not exist")

}
```

# Save both sigmoid and ascending colon counts files in new directory

```{r}
setwd('/Users/CrystalRubalcava/Desktop/final_project/')
       dir.create('allfiles')
       for (dirname in dir("1b563146-6ead-41ba-9117-c9b1c5d4127fsigmoid.htseq.counts.txt",
"0ed65bdf-cb92-47c1-8aeb-42518ce639b8ascending.htseq.counts.txt",
"1c48525e-6f1c-4ca0-9bb4-a9350cbca89fascending.htseq.counts.txt",
"2abfe58f-f168-413f-a56f-4c3c2aedbe3dascending.htseq.counts.txt",
"2f05c173-adfa-40c3-baf8-02563270ff3eascending.htseq.counts.txt",
"4e7c6811-88e4-4bb7-a88f-7491dfa6d072ascending.htseq.counts.txt",
"5ac3599c-0254-4931-8dc8-3c3294be3cd7sigmoid.htseq.counts.txt",
"5b9b9a3d-51bf-4f62-bf19-7c7ea0267030ascending.htseq.counts.txt",
"5e2b0dc5-c09b-4334-9f2f-c8e75380d45csigmoid.htseq.counts.txt",
"05eef9f8-a246-403a-b0be-07d274b6f93asigmoid.htseq.counts.txt",
"6ae2dd6c-2a39-411f-a1fc-11e0e6e82165sigmoid.htseq.counts.txt",
"6e2db920-dc3e-4a74-8cdb-470cb61e2facsigmoid.htseq.counts.txt",
"6f4f4e5d-d81e-402e-859f-3ee580a8bbdeascending.htseq.counts.txt",
"6f90946a-0a30-49e8-8699-7a8890c01aedascending.htseq.counts.txt",
"7b2cd944-1cd6-4107-8aa6-11913ee32257sigmoid.htseq.counts.txt",
"08dd2c8c-537f-4d02-a4b8-9c123156f0d4ascending.htseq.counts.txt",
"8e0528dd-5f85-4f48-937c-9e1455fbda78ascending.htseq.counts.txt",
"9c64a139-1417-4465-8472-b44182874b0aascending.htseq.counts.txt",
"9e97f017-6855-4d68-bd2a-c4da3ccb1d57ascending.htseq.counts.txt",
"9f43c5bf-0fc1-4339-81a2-1d315d6940e7sigmoid.htseq.counts.txt",
"20a523cd-58e9-467d-bed5-1bce2a8574f8sigmoid.htseq.counts.txt",
"020aa019-a3a4-4055-92ee-be824a597501sigmoid.htseq.counts.txt",
"25b8756b-61b5-40f8-bbdf-7b2de810c92fascending.htseq.counts.txt",
"30cb2eed-e635-466d-85cb-6e3d00828688sigmoid.htseq.counts.txt",
"37d2cb9b-0286-43a5-9538-26a8f0818ee7ascending.htseq.counts.txt",
"056fe861-9f3b-4693-999a-44d1d7c43ab0ascending.htseq.counts.txt",
"066a17b9-c724-4390-9a5f-d46cde556de3ascending.htseq.counts.txt",
"67d1e5e4-91de-43df-b127-ffeef6070603sigmoid.htseq.counts.txt",
"73ce143e-44f1-49c6-963f-45246d8551deascending.htseq.counts.txt",
"77dbc29d-e3dd-45cc-b1d8-3bdd1711c704sigmoid.htseq.counts.txt",
"81a64df9-c073-4097-ba73-896396da3135ascending.htseq.counts.txt",
"81d8c120-144f-4ffc-9ca4-eb76ca1fc821ascending.htseq.counts.txt",
"082a0dad-65e5-49f2-955b-ca23831b2733ascending.htseq.counts.txt",
"82e00e45-734c-471f-ba97-79ec3b7e0baasigmoid.htseq.counts.txt",
"96f97dd0-3c7a-4a8c-a165-9ab14c9fcef6ascending.htseq.counts.txt",
"161caa2d-589a-4834-9073-3824031da5e6sigmoid.htseq.counts.txt",
"171f6436-748a-4072-9ef6-e90d8cd9b465ascending.htseq.counts.txt",
"0422da40-5671-48c5-bbe0-e32a476c5cdasigmoid.htseq.counts.txt",
"562e2cb3-078f-4796-b8a2-a0196713ebacsigmoid.htseq.counts.txt",
"583c83ca-b9dd-46d2-811d-a4cde176ee24sigmoid.htseq.counts.txt",
"692efd81-4aba-45fb-a7fd-35c10c79ebf2sigmoid.htseq.counts.txt",
"708a16a3-7a5e-4e27-b06b-4c3c308b11fesigmoid.htseq.counts.txt",
"789db3c8-c5cd-428d-aaef-e3f60c40bc9asigmoid.htseq.counts.txt",
"938e4a22-7ed8-4b09-aa65-0cd737beee31ascending.htseq.counts.txt",
"3254c984-f9ec-4db5-9add-94489e000a62sigmoid.htseq.counts.txt",
"3793cde5-8027-46ad-9003-6a9a43076764sigmoid.htseq.counts.txt",
"5654a36c-4d18-4746-8a4c-b7b616f99481sigmoid.htseq.counts.txt",
"7324b2d6-dd30-4f99-a101-7c3d497bbcb8sigmoid.htseq.counts.txt",
"9556ee31-e56f-4611-9d37-2b4d19841d15ascending.htseq.counts.txt",
"17510ea6-0c97-4bd0-94a4-63dd76e5b7c7sigmoid.htseq.counts.txt",
"36263f87-1956-499c-ac90-dee060c5bdd4ascending.htseq.counts.txt",
"92107b4f-bd77-4401-9065-4b9704110d44sigmoid.htseq.counts.txt",
"1580243c-8353-4c6e-a532-81121b912c21ascending.htseq.counts.txt",
"4410295f-d9fc-43b6-8064-17ec17d5fb17sigmoid.htseq.counts.txt",
"59608767-595f-402a-9f7f-356dd6e99a51sigmoid.htseq.counts.txt",
"80592959-da54-41d0-9b82-ed279be3eceasigmoid.htseq.counts.txt",
"a046b793-0eda-4c57-adfe-b8800ece1dabascending.htseq.counts.txt",
"b1a7e378-a07b-4434-8a5d-d4756b7d523cascending.htseq.counts.txt",
"b57f69a6-91ca-4131-a654-5495f6dd1131sigmoid.htseq.counts.txt",
"ba11a188-132a-4a25-b2b7-f958694976e8ascending.htseq.counts.txt",
"bdc7d801-b93b-4464-89b6-0148d066c947ascending.htseq.counts.txt",
"bf8d10e1-1241-48fa-95a2-9e97fc58c17aascending.htseq.counts.txt",
"c3f9ba64-6946-45d4-984d-b33ef2589603sigmoid.htseq.counts.txt",
"c3fe7418-c082-4c77-96f7-f22bd6210139sigmoid.htseq.counts.txt",
"c264fe3b-482b-44ec-83a4-73df565663ffsigmoid.htseq.counts.txt",
"c6972d82-17ef-4d72-8827-a5305d55f784ascending.htseq.counts.txt",
"c2357737-ad60-4603-9ce3-4b30cc45d30bascending.htseq.counts.txt",
"cecce47d-5d1a-4473-bf62-48b9bf602534ascending.htseq.counts.txt",
"d62ce057-d970-4bb0-b929-923c7bfb9e11sigmoid.htseq.counts.txt",
"d265829a-9e49-4e21-ba72-67f5ba406204ascending.htseq.counts.txt",
"d1878265-460d-4768-a67d-73d8d5a315b7ascending.htseq.counts.txt",
"d5607680-758b-4ee5-ae0f-a61f7c3133c1ascending.htseq.counts.txt",
"db9a7c76-8e42-4f1a-81a3-a9d4eb5365aaascending.htseq.counts.txt",
"de796614-444b-4e3e-b4e6-fb3a78ef6f65sigmoid.htseq.counts.txt",
"e02d06a3-99f9-49ae-b3b0-c4427951789dascending.htseq.counts.txt",
"e158f016-7605-45b7-8e4f-bbe313fc461cascending.htseq.counts.txt",
"e82223ad-33c0-47fd-b0f2-982da64d0cb2ascending.htseq.counts.txt",
"ec78640c-f4de-4d18-bf7c-9e5391feb915ascending.htseq.counts.txt",
"ee4dcccc-514b-4cc6-ae63-6ed3e7519a40ascending.htseq.counts.txt",
"ef4fdb47-ab17-4055-b8a5-ec3c2a4b7041ascending.htseq.counts.txt",
"f5c9ea63-ff66-441a-9a6b-055fdcd7cae9ascending.htseq.counts.txt",
"f36f74a9-97b4-4913-86e2-56ebaf55f006ascending.htseq.counts.txt",
"f38b2f21-c5a5-4699-9727-eae9c96aac55sigmoid.htseq.counts.txt",
"f346f2d2-285c-455c-ba34-ea8eec3fa881sigmoid.htseq.counts.txt",
"fabefb10-5546-4017-8ea1-29982a10fb3cascending.htseq.counts.txt")
{  
        file <- list.files(paste0(getwd(),c("1b563146-6ead-41ba-9117-c9b1c5d4127fsigmoid.htseq.counts.txt",
"0ed65bdf-cb92-47c1-8aeb-42518ce639b8ascending.htseq.counts.txt",
"1c48525e-6f1c-4ca0-9bb4-a9350cbca89fascending.htseq.counts.txt",
"2abfe58f-f168-413f-a56f-4c3c2aedbe3dascending.htseq.counts.txt",
"2f05c173-adfa-40c3-baf8-02563270ff3eascending.htseq.counts.txt",
"4e7c6811-88e4-4bb7-a88f-7491dfa6d072ascending.htseq.counts.txt",
"5ac3599c-0254-4931-8dc8-3c3294be3cd7sigmoid.htseq.counts.txt",
"5b9b9a3d-51bf-4f62-bf19-7c7ea0267030ascending.htseq.counts.txt",
"5e2b0dc5-c09b-4334-9f2f-c8e75380d45csigmoid.htseq.counts.txt",
"05eef9f8-a246-403a-b0be-07d274b6f93asigmoid.htseq.counts.txt",
"6ae2dd6c-2a39-411f-a1fc-11e0e6e82165sigmoid.htseq.counts.txt",
"6e2db920-dc3e-4a74-8cdb-470cb61e2facsigmoid.htseq.counts.txt",
"6f4f4e5d-d81e-402e-859f-3ee580a8bbdeascending.htseq.counts.txt",
"6f90946a-0a30-49e8-8699-7a8890c01aedascending.htseq.counts.txt",
"7b2cd944-1cd6-4107-8aa6-11913ee32257sigmoid.htseq.counts.txt",
"08dd2c8c-537f-4d02-a4b8-9c123156f0d4ascending.htseq.counts.txt",
"8e0528dd-5f85-4f48-937c-9e1455fbda78ascending.htseq.counts.txt",
"9c64a139-1417-4465-8472-b44182874b0aascending.htseq.counts.txt",
"9e97f017-6855-4d68-bd2a-c4da3ccb1d57ascending.htseq.counts.txt",
"9f43c5bf-0fc1-4339-81a2-1d315d6940e7sigmoid.htseq.counts.txt",
"20a523cd-58e9-467d-bed5-1bce2a8574f8sigmoid.htseq.counts.txt",
"020aa019-a3a4-4055-92ee-be824a597501sigmoid.htseq.counts.txt",
"25b8756b-61b5-40f8-bbdf-7b2de810c92fascending.htseq.counts.txt",
"30cb2eed-e635-466d-85cb-6e3d00828688sigmoid.htseq.counts.txt",
"37d2cb9b-0286-43a5-9538-26a8f0818ee7ascending.htseq.counts.txt",
"056fe861-9f3b-4693-999a-44d1d7c43ab0ascending.htseq.counts.txt",
"066a17b9-c724-4390-9a5f-d46cde556de3ascending.htseq.counts.txt",
"67d1e5e4-91de-43df-b127-ffeef6070603sigmoid.htseq.counts.txt",
"73ce143e-44f1-49c6-963f-45246d8551deascending.htseq.counts.txt",
"77dbc29d-e3dd-45cc-b1d8-3bdd1711c704sigmoid.htseq.counts.txt",
"81a64df9-c073-4097-ba73-896396da3135ascending.htseq.counts.txt",
"81d8c120-144f-4ffc-9ca4-eb76ca1fc821ascending.htseq.counts.txt",
"082a0dad-65e5-49f2-955b-ca23831b2733ascending.htseq.counts.txt",
"82e00e45-734c-471f-ba97-79ec3b7e0baasigmoid.htseq.counts.txt",
"96f97dd0-3c7a-4a8c-a165-9ab14c9fcef6ascending.htseq.counts.txt",
"161caa2d-589a-4834-9073-3824031da5e6sigmoid.htseq.counts.txt",
"171f6436-748a-4072-9ef6-e90d8cd9b465ascending.htseq.counts.txt",
"0422da40-5671-48c5-bbe0-e32a476c5cdasigmoid.htseq.counts.txt",
"562e2cb3-078f-4796-b8a2-a0196713ebacsigmoid.htseq.counts.txt",
"583c83ca-b9dd-46d2-811d-a4cde176ee24sigmoid.htseq.counts.txt",
"692efd81-4aba-45fb-a7fd-35c10c79ebf2sigmoid.htseq.counts.txt",
"708a16a3-7a5e-4e27-b06b-4c3c308b11fesigmoid.htseq.counts.txt",
"789db3c8-c5cd-428d-aaef-e3f60c40bc9asigmoid.htseq.counts.txt",
"938e4a22-7ed8-4b09-aa65-0cd737beee31ascending.htseq.counts.txt",
"3254c984-f9ec-4db5-9add-94489e000a62sigmoid.htseq.counts.txt",
"3793cde5-8027-46ad-9003-6a9a43076764sigmoid.htseq.counts.txt",
"5654a36c-4d18-4746-8a4c-b7b616f99481sigmoid.htseq.counts.txt",
"7324b2d6-dd30-4f99-a101-7c3d497bbcb8sigmoid.htseq.counts.txt",
"9556ee31-e56f-4611-9d37-2b4d19841d15ascending.htseq.counts.txt",
"17510ea6-0c97-4bd0-94a4-63dd76e5b7c7sigmoid.htseq.counts.txt",
"36263f87-1956-499c-ac90-dee060c5bdd4ascending.htseq.counts.txt",
"92107b4f-bd77-4401-9065-4b9704110d44sigmoid.htseq.counts.txt",
"1580243c-8353-4c6e-a532-81121b912c21ascending.htseq.counts.txt",
"4410295f-d9fc-43b6-8064-17ec17d5fb17sigmoid.htseq.counts.txt",
"59608767-595f-402a-9f7f-356dd6e99a51sigmoid.htseq.counts.txt",
"80592959-da54-41d0-9b82-ed279be3eceasigmoid.htseq.counts.txt",
"a046b793-0eda-4c57-adfe-b8800ece1dabascending.htseq.counts.txt",
"b1a7e378-a07b-4434-8a5d-d4756b7d523cascending.htseq.counts.txt",
"b57f69a6-91ca-4131-a654-5495f6dd1131sigmoid.htseq.counts.txt",
"ba11a188-132a-4a25-b2b7-f958694976e8ascending.htseq.counts.txt",
"bdc7d801-b93b-4464-89b6-0148d066c947ascending.htseq.counts.txt",
"bf8d10e1-1241-48fa-95a2-9e97fc58c17aascending.htseq.counts.txt",
"c3f9ba64-6946-45d4-984d-b33ef2589603sigmoid.htseq.counts.txt",
"c3fe7418-c082-4c77-96f7-f22bd6210139sigmoid.htseq.counts.txt",
"c264fe3b-482b-44ec-83a4-73df565663ffsigmoid.htseq.counts.txt",
"c6972d82-17ef-4d72-8827-a5305d55f784ascending.htseq.counts.txt",
"c2357737-ad60-4603-9ce3-4b30cc45d30bascending.htseq.counts.txt",
"cecce47d-5d1a-4473-bf62-48b9bf602534ascending.htseq.counts.txt",
"d62ce057-d970-4bb0-b929-923c7bfb9e11sigmoid.htseq.counts.txt",
"d265829a-9e49-4e21-ba72-67f5ba406204ascending.htseq.counts.txt",
"d1878265-460d-4768-a67d-73d8d5a315b7ascending.htseq.counts.txt",
"d5607680-758b-4ee5-ae0f-a61f7c3133c1ascending.htseq.counts.txt",
"db9a7c76-8e42-4f1a-81a3-a9d4eb5365aaascending.htseq.counts.txt",
"de796614-444b-4e3e-b4e6-fb3a78ef6f65sigmoid.htseq.counts.txt",
"e02d06a3-99f9-49ae-b3b0-c4427951789dascending.htseq.counts.txt",
"e158f016-7605-45b7-8e4f-bbe313fc461cascending.htseq.counts.txt",
"e82223ad-33c0-47fd-b0f2-982da64d0cb2ascending.htseq.counts.txt",
"ec78640c-f4de-4d18-bf7c-9e5391feb915ascending.htseq.counts.txt",
"ee4dcccc-514b-4cc6-ae63-6ed3e7519a40ascending.htseq.counts.txt",
"ef4fdb47-ab17-4055-b8a5-ec3c2a4b7041ascending.htseq.counts.txt",
"f5c9ea63-ff66-441a-9a6b-055fdcd7cae9ascending.htseq.counts.txt",
"f36f74a9-97b4-4913-86e2-56ebaf55f006ascending.htseq.counts.txt",
"f38b2f21-c5a5-4699-9727-eae9c96aac55sigmoid.htseq.counts.txt",
"f346f2d2-285c-455c-ba34-ea8eec3fa881sigmoid.htseq.counts.txt",
"fabefb10-5546-4017-8ea1-29982a10fb3cascending.htseq.counts.txt"),pattern = '*.txt'),  
        file.copy(paste0(getwd(),c("1b563146-6ead-41ba-9117-c9b1c5d4127fsigmoid.htseq.counts.txt",
"0ed65bdf-cb92-47c1-8aeb-42518ce639b8ascending.htseq.counts.txt",
"1c48525e-6f1c-4ca0-9bb4-a9350cbca89fascending.htseq.counts.txt",
"2abfe58f-f168-413f-a56f-4c3c2aedbe3dascending.htseq.counts.txt",
"2f05c173-adfa-40c3-baf8-02563270ff3eascending.htseq.counts.txt",
"4e7c6811-88e4-4bb7-a88f-7491dfa6d072ascending.htseq.counts.txt",
"5ac3599c-0254-4931-8dc8-3c3294be3cd7sigmoid.htseq.counts.txt",
"5b9b9a3d-51bf-4f62-bf19-7c7ea0267030ascending.htseq.counts.txt",
"5e2b0dc5-c09b-4334-9f2f-c8e75380d45csigmoid.htseq.counts.txt",
"05eef9f8-a246-403a-b0be-07d274b6f93asigmoid.htseq.counts.txt",
"6ae2dd6c-2a39-411f-a1fc-11e0e6e82165sigmoid.htseq.counts.txt",
"6e2db920-dc3e-4a74-8cdb-470cb61e2facsigmoid.htseq.counts.txt",
"6f4f4e5d-d81e-402e-859f-3ee580a8bbdeascending.htseq.counts.txt",
"6f90946a-0a30-49e8-8699-7a8890c01aedascending.htseq.counts.txt",
"7b2cd944-1cd6-4107-8aa6-11913ee32257sigmoid.htseq.counts.txt",
"08dd2c8c-537f-4d02-a4b8-9c123156f0d4ascending.htseq.counts.txt",
"8e0528dd-5f85-4f48-937c-9e1455fbda78ascending.htseq.counts.txt",
"9c64a139-1417-4465-8472-b44182874b0aascending.htseq.counts.txt",
"9e97f017-6855-4d68-bd2a-c4da3ccb1d57ascending.htseq.counts.txt",
"9f43c5bf-0fc1-4339-81a2-1d315d6940e7sigmoid.htseq.counts.txt",
"20a523cd-58e9-467d-bed5-1bce2a8574f8sigmoid.htseq.counts.txt",
"020aa019-a3a4-4055-92ee-be824a597501sigmoid.htseq.counts.txt",
"25b8756b-61b5-40f8-bbdf-7b2de810c92fascending.htseq.counts.txt",
"30cb2eed-e635-466d-85cb-6e3d00828688sigmoid.htseq.counts.txt",
"37d2cb9b-0286-43a5-9538-26a8f0818ee7ascending.htseq.counts.txt",
"056fe861-9f3b-4693-999a-44d1d7c43ab0ascending.htseq.counts.txt",
"066a17b9-c724-4390-9a5f-d46cde556de3ascending.htseq.counts.txt",
"67d1e5e4-91de-43df-b127-ffeef6070603sigmoid.htseq.counts.txt",
"73ce143e-44f1-49c6-963f-45246d8551deascending.htseq.counts.txt",
"77dbc29d-e3dd-45cc-b1d8-3bdd1711c704sigmoid.htseq.counts.txt",
"81a64df9-c073-4097-ba73-896396da3135ascending.htseq.counts.txt",
"81d8c120-144f-4ffc-9ca4-eb76ca1fc821ascending.htseq.counts.txt",
"082a0dad-65e5-49f2-955b-ca23831b2733ascending.htseq.counts.txt",
"82e00e45-734c-471f-ba97-79ec3b7e0baasigmoid.htseq.counts.txt",
"96f97dd0-3c7a-4a8c-a165-9ab14c9fcef6ascending.htseq.counts.txt",
"161caa2d-589a-4834-9073-3824031da5e6sigmoid.htseq.counts.txt",
"171f6436-748a-4072-9ef6-e90d8cd9b465ascending.htseq.counts.txt",
"0422da40-5671-48c5-bbe0-e32a476c5cdasigmoid.htseq.counts.txt",
"562e2cb3-078f-4796-b8a2-a0196713ebacsigmoid.htseq.counts.txt",
"583c83ca-b9dd-46d2-811d-a4cde176ee24sigmoid.htseq.counts.txt",
"692efd81-4aba-45fb-a7fd-35c10c79ebf2sigmoid.htseq.counts.txt",
"708a16a3-7a5e-4e27-b06b-4c3c308b11fesigmoid.htseq.counts.txt",
"789db3c8-c5cd-428d-aaef-e3f60c40bc9asigmoid.htseq.counts.txt",
"938e4a22-7ed8-4b09-aa65-0cd737beee31ascending.htseq.counts.txt",
"3254c984-f9ec-4db5-9add-94489e000a62sigmoid.htseq.counts.txt",
"3793cde5-8027-46ad-9003-6a9a43076764sigmoid.htseq.counts.txt",
"5654a36c-4d18-4746-8a4c-b7b616f99481sigmoid.htseq.counts.txt",
"7324b2d6-dd30-4f99-a101-7c3d497bbcb8sigmoid.htseq.counts.txt",
"9556ee31-e56f-4611-9d37-2b4d19841d15ascending.htseq.counts.txt",
"17510ea6-0c97-4bd0-94a4-63dd76e5b7c7sigmoid.htseq.counts.txt",
"36263f87-1956-499c-ac90-dee060c5bdd4ascending.htseq.counts.txt",
"92107b4f-bd77-4401-9065-4b9704110d44sigmoid.htseq.counts.txt",
"1580243c-8353-4c6e-a532-81121b912c21ascending.htseq.counts.txt",
"4410295f-d9fc-43b6-8064-17ec17d5fb17sigmoid.htseq.counts.txt",
"59608767-595f-402a-9f7f-356dd6e99a51sigmoid.htseq.counts.txt",
"80592959-da54-41d0-9b82-ed279be3eceasigmoid.htseq.counts.txt",
"a046b793-0eda-4c57-adfe-b8800ece1dabascending.htseq.counts.txt",
"b1a7e378-a07b-4434-8a5d-d4756b7d523cascending.htseq.counts.txt",
"b57f69a6-91ca-4131-a654-5495f6dd1131sigmoid.htseq.counts.txt",
"ba11a188-132a-4a25-b2b7-f958694976e8ascending.htseq.counts.txt",
"bdc7d801-b93b-4464-89b6-0148d066c947ascending.htseq.counts.txt",
"bf8d10e1-1241-48fa-95a2-9e97fc58c17aascending.htseq.counts.txt",
"c3f9ba64-6946-45d4-984d-b33ef2589603sigmoid.htseq.counts.txt",
"c3fe7418-c082-4c77-96f7-f22bd6210139sigmoid.htseq.counts.txt",
"c264fe3b-482b-44ec-83a4-73df565663ffsigmoid.htseq.counts.txt",
"c6972d82-17ef-4d72-8827-a5305d55f784ascending.htseq.counts.txt",
"c2357737-ad60-4603-9ce3-4b30cc45d30bascending.htseq.counts.txt",
"cecce47d-5d1a-4473-bf62-48b9bf602534ascending.htseq.counts.txt",
"d62ce057-d970-4bb0-b929-923c7bfb9e11sigmoid.htseq.counts.txt",
"d265829a-9e49-4e21-ba72-67f5ba406204ascending.htseq.counts.txt",
"d1878265-460d-4768-a67d-73d8d5a315b7ascending.htseq.counts.txt",
"d5607680-758b-4ee5-ae0f-a61f7c3133c1ascending.htseq.counts.txt",
"db9a7c76-8e42-4f1a-81a3-a9d4eb5365aaascending.htseq.counts.txt",
"de796614-444b-4e3e-b4e6-fb3a78ef6f65sigmoid.htseq.counts.txt",
"e02d06a3-99f9-49ae-b3b0-c4427951789dascending.htseq.counts.txt",
"e158f016-7605-45b7-8e4f-bbe313fc461cascending.htseq.counts.txt",
"e82223ad-33c0-47fd-b0f2-982da64d0cb2ascending.htseq.counts.txt",
"ec78640c-f4de-4d18-bf7c-9e5391feb915ascending.htseq.counts.txt",
"ee4dcccc-514b-4cc6-ae63-6ed3e7519a40ascending.htseq.counts.txt",
"ef4fdb47-ab17-4055-b8a5-ec3c2a4b7041ascending.htseq.counts.txt",
"f5c9ea63-ff66-441a-9a6b-055fdcd7cae9ascending.htseq.counts.txt",
"f36f74a9-97b4-4913-86e2-56ebaf55f006ascending.htseq.counts.txt",
"f38b2f21-c5a5-4699-9727-eae9c96aac55sigmoid.htseq.counts.txt",
"f346f2d2-285c-455c-ba34-ea8eec3fa881sigmoid.htseq.counts.txt",
"fabefb10-5546-4017-8ea1-29982a10fb3cascending.htseq.counts.txt"), allfiles,files),allfiles)

}
```

# All files from ```allfiles``` dir are listed below and can be found collectively until ```files```
```{r}
setwd('/Users/CrystalRubalcava/Desktop/final_project/')
       dir.create('allfiles')
files <- c("1b563146-6ead-41ba-9117-c9b1c5d4127fsigmoid.htseq.counts.txt",
"0ed65bdf-cb92-47c1-8aeb-42518ce639b8ascending.htseq.counts.txt",
"1c48525e-6f1c-4ca0-9bb4-a9350cbca89fascending.htseq.counts.txt",
"2abfe58f-f168-413f-a56f-4c3c2aedbe3dascending.htseq.counts.txt",
"2f05c173-adfa-40c3-baf8-02563270ff3eascending.htseq.counts.txt",
"4e7c6811-88e4-4bb7-a88f-7491dfa6d072ascending.htseq.counts.txt",
"5ac3599c-0254-4931-8dc8-3c3294be3cd7sigmoid.htseq.counts.txt",
"5b9b9a3d-51bf-4f62-bf19-7c7ea0267030ascending.htseq.counts.txt",
"5e2b0dc5-c09b-4334-9f2f-c8e75380d45csigmoid.htseq.counts.txt",
"05eef9f8-a246-403a-b0be-07d274b6f93asigmoid.htseq.counts.txt",
"6ae2dd6c-2a39-411f-a1fc-11e0e6e82165sigmoid.htseq.counts.txt",
"6e2db920-dc3e-4a74-8cdb-470cb61e2facsigmoid.htseq.counts.txt",
"6f4f4e5d-d81e-402e-859f-3ee580a8bbdeascending.htseq.counts.txt",
"6f90946a-0a30-49e8-8699-7a8890c01aedascending.htseq.counts.txt",
"7b2cd944-1cd6-4107-8aa6-11913ee32257sigmoid.htseq.counts.txt",
"08dd2c8c-537f-4d02-a4b8-9c123156f0d4ascending.htseq.counts.txt",
"8e0528dd-5f85-4f48-937c-9e1455fbda78ascending.htseq.counts.txt",
"9c64a139-1417-4465-8472-b44182874b0aascending.htseq.counts.txt",
"9e97f017-6855-4d68-bd2a-c4da3ccb1d57ascending.htseq.counts.txt",
"9f43c5bf-0fc1-4339-81a2-1d315d6940e7sigmoid.htseq.counts.txt",
"20a523cd-58e9-467d-bed5-1bce2a8574f8sigmoid.htseq.counts.txt",
"020aa019-a3a4-4055-92ee-be824a597501sigmoid.htseq.counts.txt",
"25b8756b-61b5-40f8-bbdf-7b2de810c92fascending.htseq.counts.txt",
"30cb2eed-e635-466d-85cb-6e3d00828688sigmoid.htseq.counts.txt",
"37d2cb9b-0286-43a5-9538-26a8f0818ee7ascending.htseq.counts.txt",
"056fe861-9f3b-4693-999a-44d1d7c43ab0ascending.htseq.counts.txt",
"066a17b9-c724-4390-9a5f-d46cde556de3ascending.htseq.counts.txt",
"67d1e5e4-91de-43df-b127-ffeef6070603sigmoid.htseq.counts.txt",
"73ce143e-44f1-49c6-963f-45246d8551deascending.htseq.counts.txt",
"77dbc29d-e3dd-45cc-b1d8-3bdd1711c704sigmoid.htseq.counts.txt",
"81a64df9-c073-4097-ba73-896396da3135ascending.htseq.counts.txt",
"81d8c120-144f-4ffc-9ca4-eb76ca1fc821ascending.htseq.counts.txt",
"082a0dad-65e5-49f2-955b-ca23831b2733ascending.htseq.counts.txt",
"82e00e45-734c-471f-ba97-79ec3b7e0baasigmoid.htseq.counts.txt",
"96f97dd0-3c7a-4a8c-a165-9ab14c9fcef6ascending.htseq.counts.txt",
"161caa2d-589a-4834-9073-3824031da5e6sigmoid.htseq.counts.txt",
"171f6436-748a-4072-9ef6-e90d8cd9b465ascending.htseq.counts.txt",
"0422da40-5671-48c5-bbe0-e32a476c5cdasigmoid.htseq.counts.txt",
"562e2cb3-078f-4796-b8a2-a0196713ebacsigmoid.htseq.counts.txt",
"583c83ca-b9dd-46d2-811d-a4cde176ee24sigmoid.htseq.counts.txt",
"692efd81-4aba-45fb-a7fd-35c10c79ebf2sigmoid.htseq.counts.txt",
"708a16a3-7a5e-4e27-b06b-4c3c308b11fesigmoid.htseq.counts.txt",
"789db3c8-c5cd-428d-aaef-e3f60c40bc9asigmoid.htseq.counts.txt",
"938e4a22-7ed8-4b09-aa65-0cd737beee31ascending.htseq.counts.txt",
"3254c984-f9ec-4db5-9add-94489e000a62sigmoid.htseq.counts.txt",
"3793cde5-8027-46ad-9003-6a9a43076764sigmoid.htseq.counts.txt",
"5654a36c-4d18-4746-8a4c-b7b616f99481sigmoid.htseq.counts.txt",
"7324b2d6-dd30-4f99-a101-7c3d497bbcb8sigmoid.htseq.counts.txt",
"9556ee31-e56f-4611-9d37-2b4d19841d15ascending.htseq.counts.txt",
"17510ea6-0c97-4bd0-94a4-63dd76e5b7c7sigmoid.htseq.counts.txt",
"36263f87-1956-499c-ac90-dee060c5bdd4ascending.htseq.counts.txt",
"92107b4f-bd77-4401-9065-4b9704110d44sigmoid.htseq.counts.txt",
"1580243c-8353-4c6e-a532-81121b912c21ascending.htseq.counts.txt",
"4410295f-d9fc-43b6-8064-17ec17d5fb17sigmoid.htseq.counts.txt",
"59608767-595f-402a-9f7f-356dd6e99a51sigmoid.htseq.counts.txt",
"80592959-da54-41d0-9b82-ed279be3eceasigmoid.htseq.counts.txt",
"a046b793-0eda-4c57-adfe-b8800ece1dabascending.htseq.counts.txt",
"b1a7e378-a07b-4434-8a5d-d4756b7d523cascending.htseq.counts.txt",
"b57f69a6-91ca-4131-a654-5495f6dd1131sigmoid.htseq.counts.txt",
"ba11a188-132a-4a25-b2b7-f958694976e8ascending.htseq.counts.txt",
"bdc7d801-b93b-4464-89b6-0148d066c947ascending.htseq.counts.txt",
"bf8d10e1-1241-48fa-95a2-9e97fc58c17aascending.htseq.counts.txt",
"c3f9ba64-6946-45d4-984d-b33ef2589603sigmoid.htseq.counts.txt",
"c3fe7418-c082-4c77-96f7-f22bd6210139sigmoid.htseq.counts.txt",
"c264fe3b-482b-44ec-83a4-73df565663ffsigmoid.htseq.counts.txt",
"c6972d82-17ef-4d72-8827-a5305d55f784ascending.htseq.counts.txt",
"c2357737-ad60-4603-9ce3-4b30cc45d30bascending.htseq.counts.txt",
"cecce47d-5d1a-4473-bf62-48b9bf602534ascending.htseq.counts.txt",
"d62ce057-d970-4bb0-b929-923c7bfb9e11sigmoid.htseq.counts.txt",
"d265829a-9e49-4e21-ba72-67f5ba406204ascending.htseq.counts.txt",
"d1878265-460d-4768-a67d-73d8d5a315b7ascending.htseq.counts.txt",
"d5607680-758b-4ee5-ae0f-a61f7c3133c1ascending.htseq.counts.txt",
"db9a7c76-8e42-4f1a-81a3-a9d4eb5365aaascending.htseq.counts.txt",
"de796614-444b-4e3e-b4e6-fb3a78ef6f65sigmoid.htseq.counts.txt",
"e02d06a3-99f9-49ae-b3b0-c4427951789dascending.htseq.counts.txt",
"e158f016-7605-45b7-8e4f-bbe313fc461cascending.htseq.counts.txt",
"e82223ad-33c0-47fd-b0f2-982da64d0cb2ascending.htseq.counts.txt",
"ec78640c-f4de-4d18-bf7c-9e5391feb915ascending.htseq.counts.txt",
"ee4dcccc-514b-4cc6-ae63-6ed3e7519a40ascending.htseq.counts.txt",
"ef4fdb47-ab17-4055-b8a5-ec3c2a4b7041ascending.htseq.counts.txt",
"f5c9ea63-ff66-441a-9a6b-055fdcd7cae9ascending.htseq.counts.txt",
"f36f74a9-97b4-4913-86e2-56ebaf55f006ascending.htseq.counts.txt",
"f38b2f21-c5a5-4699-9727-eae9c96aac55sigmoid.htseq.counts.txt",
"f346f2d2-285c-455c-ba34-ea8eec3fa881sigmoid.htseq.counts.txt",
"fabefb10-5546-4017-8ea1-29982a10fb3cascending.htseq.counts.txt"
)

```


# Update: Bring in clinical data to map TCGA IDs from json file. 

```{r}
# Map TCGA id from clinical data in the clinical.csv file from the gdc clinical cases file and save edited file as `ascending_sigmoid.csv`

directory <- '/Users/CrystalRubalcava/Desktop/final_project/allfiles'
# use read.table and specify tab delimited 

colnames(case_id) <- c('filename','TCGA_id')

```

# Final Updates: Analyzing RNA-seq data with `DESeq2` based on the Tutorial
# RNA-Seq gene profiling using HTSeq-count files from Stage II colon cancer patients
DESeqDataSet used to generate counts from htseq-counts
Side note: HTSeq is a python framework that is used to work with sequencing data and mapping information

DESeqDataSet used to generate counts from htseq-counts
Generate count tables from RNA read mapping and record gene expression from genomes and metagenomes.

We will be counting the reads and estimating expression genes or genomic regions

Installation of required packages
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("rnaseqGene")

library("DESeq2")

```



# Specify which files to read using list.files and select the files with ```htseq``` using grep
Here ascending will group all counts from patients with tumor origin sites in the ascending colon. All patients with tumor origin sites in the sigmoid colon will be grouped in sigmoid. 
```{r}
sampleFiles <- grep("ascending",list.files(directory),value=TRUE)
sampleCondition <- sub("(.*ascending).*","\\1",sampleFiles)
sampleTable <- data.frame(sampleName = sampleFiles,
                          fileName = sampleFiles,
                          condition = sampleCondition)
sampleTable$condition <- factor(sampleTable$condition)
```


```{r}
final_project <- grep("tumor_origin_site",list.files(directory),value=TRUE)
sampleCondition <- sub("(.*tumor_origin_site).*","\\1",final_project)
sampleTable <- data.frame(sampleName = final_project,
                          fileName = final_project,
                          condition = sampleCondition)
sampleTable$condition <- factor(sampleTable$condition)
```

# 3. Install 'SummarizedExperiment' package that contains DESeq2
```{r}
library("DESeq2")
ddsHTSeq <- DESeqDataSetFromHTSeqCount(sampleTable = sampleTable,
                                       directory = directory,
                                       design= ~ condition)
ddsHTSeq
dds <- DESeq(ddsHTSeq)
resultsNames(dds) # lists the coefficients
```