---
title: "Data Prep for DESeq2"
output: html_notebook
---

## A. Prep Data for DESEQ2

## 1. Created two directories to hold htseq count files for sigmoid tumor origin site (sig) and ascending tumor origin site (asc). Unzip all count files using linux.
```{bash}
mkdir ~/final_project/sig
cd ~/final_project/sigmoid
cp ~/final_project/sigmoid/*.counts ~/final_project/sig
gunzip -r ~/final_project/sig
mkdir ~/final_project/asc
cd ~/final_project/ascending
cp ~/final_project/ascending/*.counts ~/final_project/asc
gunzip -r ~/final_project/asc

```
# 2. Rename files in in sig and asc files to add the condition to the file name to prep it for the sample table we will create later for the DESEQ analysis
```{bash}
cd ~/final_project/sig
for i in *; do mv "$i" sig_"$i"; done
```

```{bash}
cd ~/final_project/asc
for i in *; do mv "$i" asc_"$i"; done
```

# 3. Add all renamed count files into one directory - 'allcounts' to prep for analysis 
```{bash}
mkdir ~/final_project/allcounts
cp ~/final_project/asc/*.counts ~/final_project/allcounts
cp ~/final_project/sig/*.counts ~/final_project/allcounts
```

# 4. Get list of all files in directory

```{r}
#for sigmoid tumor origin site files
setwd("~/final_project/sig")
files = list.files(path="~/final_project/sig", pattern=".counts")

#Merge the first to files and store
file1 = read.table(files[1], col.names=c("gene_id",files[1]))
file2 = read.table(files[2], col.names=c("gene_id",files[2]))
combined.file = merge (file1, file2, by=c("gene_id"))

#For loop to merge contents of remaining files
for(i in 3:length(files))
{
file = read.table(files[i],col.names=c("gene_id",files[i]))
combined.file <- merge(combined.file, file, by=c("gene_id"))
}
write.table(combined.file, file = "htseq_sig.csv", sep = ",", row.names = FALSE)
```

```{r}
# for ascending tumor origin site files
setwd("~/final_project/asc")
files = list.files(path="~/final_project/asc", pattern=".counts")

#Merge the first to files and store
file1 = read.table(files[1], col.names=c("gene_id",files[1]))
file2 = read.table(files[2], col.names=c("gene_id",files[2]))
combined.file = merge (file1, file2, by=c("gene_id"))

#For loop to merge contents of remaining files
for(i in 3:length(files))
{
file = read.table(files[i],col.names=c("gene_id",files[i]))
combined.file <- merge(combined.file, file, by=c("gene_id"))
}
write.table(combined.file, file = "htseq_asc.csv", sep = ",", row.names = FALSE)
```

```{r}
# for ascending tumor origin site files
setwd("~/final_project/allcounts")
files = list.files(path="~/final_project/allcounts", pattern=".counts")

#Merge the first to files and store
file1 = read.table(files[1], col.names=c("gene_id",files[1]))
file2 = read.table(files[2], col.names=c("gene_id",files[2]))
combined.file = merge (file1, file2, by=c("gene_id"))

#For loop to merge contents of remaining files
for(i in 3:length(files))
{
file = read.table(files[i],col.names=c("gene_id",files[i]))
combined.file <- merge(combined.file, file, by=c("gene_id"))
}
write.table(combined.file, file = "htseq_all.csv", sep = ",", row.names = FALSE)
```

# 5. remove rows 2-6 from all files as they are not needed manually
# 6. Rename file names by editting long file names manually
# 7. Use excel vlookup function to add gender assignment to file name for simplicity of building the data frame when loading the data into DESeq2. This was done by using clinical.csv data from both the sigmoid and ascending data pulls from the GCD portal. All needed files can be found in the google drive folder. 

## B. Load Data into DESEQ2

# 1. Using HTSeq counts as input, DESeqDataSetFromHTSeqCount, create sample table for all counts including tumor origin sites in the sigmoid (sig ) and ascending colon(asc).
# May need to rename files names manually for simplicity 

```{r}
library("stringr")
directory <- "~/final_project/allcounts/"
sampleFiles <- grep("counts",list.files(directory),value=TRUE)
#sampleCondition <- sub("^(\\d{3}).*$","\\1",sampleFiles) #if the code below does not work, use this to pull the first 3 letter of the file name to specify the condition
sampleCondition <- substr(sampleFiles, 0, 3) #first three letters of the file name contain the condition of the sample
#sampleName <- sub("^(\\d{8}).*$","\\1",sampleFiles) #if the code below does not work, use this to pull the first 8 letter of the file name to specify the condition
sampleName <- substr(sampleFiles, 0, 5) # file name is the condition and number related to the file
sampleGender <- str_sub(sampleFiles, - 1, - 1) #last character of the file contains gender file sample
sampleTable <- data.frame(sampleName = sampleFiles,
                          fileName = sampleFiles,
                          condition = sampleCondition,
                          gender = sampleGender)
sampleTable$condition <- factor(sampleTable$condition)
```


